---
title: "Weekly Exercise"
author: "Jonas Meirer"
date: "23 9 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1, Part b

## Task
Create an HTML docuemtn that samples 100 values from a *log-normal distribution* (say, mu = 1, sigma = .25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in text. In general, do not just dump the R code and plots in the HTML docuement; break your exercise into sections with headings, add some text and make it readable

## Let's begin

### Data Generation

First, sample 100 values from the Log-Normal distribution:
```{r data}
lognorm <- data.frame(Values = rlnorm(100, 1, 0.25))

```

### Visualization

In order to visualize this, we first need to load the ggplot plackage. Then we can start with the actual plotting of a **histogram**:
```{r plot}
library(ggplot2)
ggBase <- ggplot(data = lognorm, aes(x=Values)) 

ggBase+ 
  geom_histogram(binwidth = 0.1) + 
  theme_bw() + 
  ggtitle("Histogram of the sampeled Log-Norm distribution")
```

We can also take a look at the continuous **density plot**:
```{r plot2}
ggBase + 
  geom_density() + 
  theme_bw() + 
  ggtitle("Density plot of the sampeled Log-Norm distribution")
```

The **characteristics** of the sampled log-norm distribution can be calculated as:
```{r characteristics}
log_norm_mean <- round(mean(lognorm$Values), digits = 4)
log_norm_sd   <- round(sd(lognorm$Values)  , digits = 4)

```

The mean is `r log_norm_mean` and the variance is `r log_norm_sd`.

Now let's check how the plots change when we move a **logarithmic scale** instead: 
```{r plot 3}
ggBase+ 
  geom_histogram(binwidth = 0.1) + 
  theme_bw() + 
  ggtitle("Histogram of the sampeled Log-Norm distribution (Log-Scale)") +
  scale_x_continuous(trans = 'log10')

```

And also the **density plot**:

```{r plot 4}
ggBase + 
  geom_density() + 
  theme_bw() + 
  ggtitle("Density plot of the sampeled Log-Norm distribution (Log-Scale)") + 
  scale_x_log10()
```

This actually looks way more like a normal distribution, which does make sense since the log-normal distribution is characterized as the probability distribution of a variable whose logarithm is normally distributed.

### End of exercise